method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
added ANOVA EMG view

datalist_EMG <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
                          read.table, stringsAsFactors = FALSE, header = TRUE)
datalist_EMG_Marker <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = "*.Markers", full.names = TRUE),
                              read.table, stringsAsFactors = FALSE, header = TRUE, skip = 1, row.names = NULL)

# new empty frame to store files into
data_EMG = data.frame(ID = character(), segment = double(), Corr = double(), 
                     Lev = double())

@@

# Figure to visualize effort ratings
# figure
FigSubjEffortPilot = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")
```

>>>>

datalist_EMG <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
                          read.table, stringsAsFactors = FALSE, header = TRUE)
datalist_EMG_Marker <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = "*.Markers", full.names = TRUE),
                              read.table, stringsAsFactors = FALSE, header = TRUE, skip = 1, row.names = NULL, sep = ",")

# new empty frame to store files into
data_EMG = data.frame(ID = character(), trigger = double(), Corr = double(), 
                     Lev = double())

@@

# Figure to visualize effort ratings
# figure
FigSubjEffortPilot = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")

### EMG

# effect of valence on EMG

EMG_view <- data_EMG %>%
  subset(data_EMG$segment == "view_neu" | data_ER$block == "view_neg")
Ratings_view$block <- as.factor(Ratings_view$block)
